% Please use this sample.tex file.
%============================================
\documentstyle[12pt]{article}
\renewcommand\floatpagefraction{0.9}
\renewcommand{\baselinestretch}{1.}
\topmargin 0.3in
\newcommand{\marg}[1]{\marginpar{\raggedright\scriptsize#1}}
\parskip=10pt
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.0in}
\setlength{\oddsidemargin}{0.0in}
\begin{document}
\pagestyle{empty}
\begin{center}
\begin{large}
{\bf Title of the Paper}
\end{large}
\end{center}

\vskip0.4in
\begin{center}
{\large \bf\underline{The name of First Author} and The Name of second Author}\\
Line1: Address of the First two Authors if they have the same address.\\
Line 2\\
Line 3\\
email: \\
\end{center}

\begin{center}
{\large \bf Name of the Third Author}\\
Line 1:Adress of the Third Author\\
Line 2\\
Line 3\\
email: 
\end{center}

\bigskip
\centerline {{\bf ABSTRACT}}
\bigskip

Here, please put your own Abstract. It should not be more than one PAGE.

Example of an Abstract: 

The class of complex modified Korteweg-de Vries (CMKdV) equations has many
applications. One form of the CMKdV equation has been used to create models 
for the nonlinear evolution of plasma waves, for the propagation of transverse 
waves in a molecular chain, and for a generalized elastic solid.
Another form of the CMKdV equation has been used for the traveling-wave and
for a double homoclinic orbit \cite{Herbst_Ablowitz_Ryan}.

In this paper we introduce sequential and parallel split-step Fourier methods
for numerical simulations of the above equation.
The parallel methods are implemented on the Origin 2000 multiprocessor computer.
Our numerical experiments have shown that the finite difference and the
inverse scattering methods give accurate results and considerable speedup.



\begin{thebibliography}{1}

\bibitem{Herbst_Ablowitz_Ryan} B. M. Herbst, M. J. Ablowitz and E. Ryan,
Numerical homoclinic instabilities and the complex modified Korteweg-de Vries eq
uation,
{\sl Comput. Phys. Commun.}, {\bf 65} (1991),
137-142.


\end{thebibliography}

\end{document}
