\documentclass[12pt]{dsa}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\textwidth=6in
 \textheight=9.5in
  \headheight.2cm
   \topmargin-0.5in
\evensidemargin0.25in
\oddsidemargin0.25in
\def\baselinestretch{1.25}\large\normalsize

\hbadness3000
\vbadness30000
\parindent=0.3in
\parskip=3pt plus 1pt minus 1pt

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{cor}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}
\setcounter{page}{1}

\begin{document}
\newcommand{\T}{\mathbb{T}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\tx}[1]{\quad\mbox{#1}\quad}
%Please put here any further newcommands.

\noindent {\tt Neural, Parallel, and Scientific Computations [CNLS-2013] 22 (2014) xx-xx}

\title[Short Title]{\mbox{}\\[1cm]Full Title}
\author{Author$^1$}
\author{Author$^2$}
\author{Author$^3$}
\begin{abstract}
\vspace{-.2cm} 
\begin{center}
$^1$Department of Mathematical Science, Florida Institute of Technology, Melbourne, Florida 32901, USA.\\
$^2$Department of Mathematics, National University of Ireland, Galway, Ireland. \\
$^3$Department of Mathematics, Tribhuvan University, 
Kirtipur, Nepal.
\end{center}
\vspace{-.2cm}
\end{abstract}
\thanks{\hspace{-.5cm}\tt
	Received December 31, 2013
	\hfill 1061-5369 \$15.00 \copyright Dynamic Publishers, Inc.}
\maketitle
\thispagestyle{empty}

{\footnotesize
\noindent{\bf ABSTRACT.} Type the abstract here

\noindent{\bf AMS (MOS) Subject Classification.} 39A10.
}

\section{FIRST SECTION}\label{s1}
%Start the first section of the paper here.

\section{SECOND SECTION}\label{s2}
%Start the second section of the paper here.

\section*{ACKNOWLEDGMENTS}
%If there are any acknowledgments to research support etc., they go here. Notice that this section is unnumbered. 

\begin{thebibliography}{9}

\bibitem{a1} J.~Appell, H.T.~Nguyen and P.~Zabreiko, Multivalued superposition operators in ideal spaces of vector functions III, {\em Indag. Math.}, 3:1--9, 1992.

\bibitem{a2} J.~Aubin and A.~Cellina, \emph{Differential Inclusions}, Springer Verlag,
New York, 1984.

\bibitem{a3} G.~Birkhoff, \emph{Lattice Theory}, {\em Amer. Math. Soc. Coll. Publ.} Vol 25, New York, 1967.

 
\end{thebibliography}

\end{document}
)
